## Author: Ian Hinds
## Date: 6 Sep 2020
## Purpose: Climate Classification

```{r message=FALSE, warning=FALSE}
library(readr)
library(elevatr)
library(tidyverse)
library(sf)
library(raster)
library(climateR)
library(USAboundaries)
library(exactextractr)
```
Pick 2-4 climate variables for a state of your choice for one month of your choice (winter,summer, spring, etc)

* Pick your climate variables based on the state and month you choose
* You can find available climate variables using (param_meta$terraclim) (use the call column)
* Implement a k-means classification for your state and your variables.
* Plot your final image using a nice color palette

```{r message=FALSE, warning=FALSE}
param_meta$terraclim

#define climate variables
params = c("tmax", "tmin","prcp", "q")

#define AOI
AOI = USAboundaries::us_states() %>% 
  filter(name == "Tennessee") 

#combine variables and extract data
#tn = getTerraClim(AOI, params, startDate = "2018-9-01")  %>%
#  stack() %>% 
#  setNames(params) 

#Warning in .Internal(socketAccept(socket, blocking, open, encoding, timeout)) :closing unused connection 125 (<-GIS5050two.utk.tennessee.edu:11091)
#Error in socketAccept(socket = socket, blocking = TRUE, open = "a+b",: all connections are in use

#plot attempt
#plot(tn) #not working out

# Prep data Attempt
#idx = which(!is.na(tn))
#v = na.omit(tn)
#vs = scale(v)

#Cluster Attempt
#E = kmeans(vs, 5, iter.max = 100)
#clus_raster = elev[[1]]
#values(clus_raster) = NA
#clus_raster[idx] <- E$cluster

# Palette Attempt, cannot complete
#palette = colorRampPalette(c("blue", "white", "red"))
#plot(vs, col = palette(256))

```

