## Author: Ian Hinds
## Date: 1-3 Sep 2020
## Purpose: First Raster

### Day 17
- Install *elevatr*
- Read in uscities.csv, filter to goleta
- Refine CRS
- Buffer 5000
- Get bounding box of buffer and make sfc then sf
- Pass bounding box to elevatr
- Define a Z
- Crop returned elevation to the bb3
- Plot raster and describe the properties
```{r message=FALSE, warning=FALSE}
library(readr)
library(elevatr)
library(tidyverse)
library(sf)
library(raster)


goleta <- read.csv("../data/uscities.csv") %>%
  filter(city %in% c("Goleta")) %>%
  st_as_sf(coords = c("lng", "lat"), crs = 4326) %>%
  st_transform(5070) %>%
  st_buffer(5000) %>%
  st_bbox() %>%
  st_as_sfc() %>%
  st_as_sf ()

#elevatr
elevation = elevatr::get_elev_raster(goleta, z=11) %>% crop(goleta)
writeRaster(elevation, filename = "../data/goleta-elevation.tif", overwrite = TRUE)

elevation = raster("../data/goleta-elevation.tif")

plot(elevation)

                         
                        


```

The raster labels higher elevations as green, and sea level as white. X and Y axis represent latitude and longitude. The color differences help visualize the topography of the Goleta area.

*****

### Day 18
```{r}
goletaelev = raster("../data/goleta-elevation.tif")

thresh = function(x) (ifelse(x <= 0, NA, 1))

cal = calc(goletaelev, thresh)

ocean = cal * goletaelev


rec = data.frame(min = seq(0, 500, 100), max = seq(100, 600, 100), lab = c(0:5))

reclass = reclassify(ocean, rec, lowerTRUE = TRUE)

st = stack(goletaelev, cal, ocean, reclass) %>%
  setNames(c("elev", "land", "coast", "topo")) 

plot(st)

```
### Day 19
```{r message=FALSE, warning=FALSE}
#load osm
library(osmdata)
library(dplyr)
# check features
#head(available_features())

#amenities
#head(available_tags("amenity"))

#shops
#head(available_tags("shop"))

#define goleta restaurants
goleta_bb = st_bbox(st) %>%
  st_as_sfc() %>%
  st_transform(4326)

goleta_rest = osmdata::opq(goleta_bb) %>%
  add_osm_feature(key = "amenity", value = "restaurant") %>%
  osmdata_sf()

print(goleta_rest)

#need to remove locations without names, extract elevations, create a leaflet map



```

