## Author: Ian Hinds
## Date: 9 Sep 2020
## Purpose: Terrain Processing

We are going to evaluate the terrain near Mount Saint Helens

* Get a representation of Mount Saint Helens using AOI::aoi_get()
* Buffer the returned polygon by a 1/2 mile
```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(whitebox)
library(elevatr)
```

```{r}
mtsh = AOI::aoi_get("Mount Saint Helens") %>%
  AOI::aoi_buffer(0.5)
```

**In a chunk with eval = FALSE**
* Get elevation for this AOI using elevatr and a zoom of 12
* Write the raster as a tif to your data folder
* Create a hillshade, slope, and aspect raster using whitebox
be intentional with you path names

```{r}
eval = FALSE
elev = elevatr::get_elev_raster(mtsh, z = 12) %>%
  crop(mtsh)

writeRaster(elev, "../data/mtsh-area-elev.tif", overwrite = TRUE)

wbt_hillshade("../data/mtsh-area-elev.tif", "../data/mtsh-area-hillshade.tif")

r = raster("../data/mtsh-area-elev.tif")
plot(r,  box = FALSE, axes = FALSE, col = gray.colors(256))

  

```

